---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ISLR)

head(Smarket)
```
```{r}
cor(Smarket[, -9])
```
```{r}
plot(Smarket$Volume)
```
```{r}
glm.fits = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Smarket, family=binomial)
summary(glm.fits)
```
```{r}
coef(glm.fits)
```
```{r}
summary(glm.fits)$coef
```
```{r}
# pulling out just the p-values 
summary(glm.fits)$coef[, 4]
```
```{r}
glm.probs = predict(glm.fits, type="response")
glm.probs[1:10]
```
```{r}
contrasts(Smarket$Direction)
```
```{r}
glm.pred = rep("Down", 1250)
glm.pred[glm.probs > .5] = "Up"
glm.pred[1:10]
```

```{r}
table(glm.pred, Smarket$Direction)
```

Training accuracy (based on the above confusion matrix): (TP + TN) / ALL
```{r}
(145 + 507) / 1250
``` 

Splitting data intro training and the test set. Years 2001 through 2004 are used for training and the remaining year - 2005 - is kept for testing.
```{r}
train = (Smarket$Year < 2005)
Smarket.2005 = Smarket[!train,]
dim(Smarket.2005)
```
```{r}
Direction.2005 = Smarket$Direction[!train]
```

Fitting logistic regression only to the training set.
```{r}
glm.fits = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, family=binomial,
               data=Smarket, subset=train)
glm.probs = predict(glm.fits, Smarket.2005, type="response")
glm.probs[1:10]
```
```{r}
glm.pred = rep("Down", 252)
glm.pred[glm.probs > .5] = "Up"
table(glm.pred, Direction.2005)
```

Accuracy on the test set:
```{r}
(77 + 44) / 252
```

Fitting logistic regression on Lag1 and Lag2 only, since they have the smallest p-value
```{r}
glm.fits = glm(Direction~Lag1+Lag2, data=Smarket, family="binomial",
               subset=train)
glm.probs = predict(glm.fits, Smarket.2005, type="response")
glm.pred = rep("Down", 252)
glm.pred[glm.probs
         > .5] = "Up"
table(glm.pred, Direction.2005)
```

Accuracy on the test set, using Lag1 and Lag2 predictors
```{r}
(35 + 106) / 252
```

Making prediction for new observations
```{r}
newdata = data.frame(Lag1=c(1.2, 1.5), Lag2=c(1.1, -0.8))
predict(glm.fits, newdata, type="response")
```

